%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Presentations/Courses Attended}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Presenter for TomoChain's Consensus Protocol for Scalability and On-chain Governance} % Role
{Dezentral Conference at Berlin Blockchain Week} % Event
{Berlin, Germany} % Location
{Sept. 2018} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {Presented the Proof-of-Stake Voting consensus protocol proposed by TomoChain, which solves the blockchain scalability and on-chain governance problem.}
	\end{cvitems}
}

\cventry
{Presenter for TomoChain's Consensus Protocol for Scalability and On-chain Governance} % Role
{GroundX Conference at Jeju island} % Event
{Berlin, Germany} % Location
{Jul. 2018} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {Presented the Proof-of-Stake Voting consensus protocol proposed by TomoChain and joined the panel discussion about blockchain consensus and security.}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{Presenter for Conference Paper: Bidirectional Mapping Between Architecture and Code for Synchronization} % Role
{14th ICSA (International Conference on Software Architecture)} % Event
{Gothenburg, Sweeden} % Location
{Apr. 2017} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {Presented an approach, which enables a bidirectional mapping between UML-based architecture model and code. This proposed mapping is part of a synchronization approach, which synchronizes code and UML-based model, using UML component-based modeling and UML state machines.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Presenter for Conference Paper: Complete Code Generation From UML State Machines} % Role
{5th MODELSWARD (International Conference on Model-Driven Engineering and Software Development)} % Event
{Porto, Portugal} % Location
{Feb. 2017} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {Presented an approach, which enables generating efficient code from UML state machines with full UML state machine features, including pseudo states and UML events. The generated code is evaluated for its runtime execution semantics conforming to the UML specification, its performance in event processing speed, and its static and dynamic memory consumption.}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{Presenter for Conference Paper: Foster Software Architect and Programmer Collaboration} % Role
{21th ICECCS (International Conference on Engineering of Complex Computer Systems)} % Event
{Dubai, UAE} % Location
{Nov. 2016} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {Presented a model-code synchronization methodological pattern, which allows model and code to be concurrently modified by software architects and programmers, respectively, and synchronizes the modifications made in the model and the code.}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{Presenter for Conference Paper: From UML State Machine to Code and Back} % Role
{36th SEW (International Software Engineering Workshop)} % Event
{Gothenburg, Sweed} % Location
{Sept. 2016} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {Presented a mapping between UML state machine elements and object-oriented code. The purpose is to provide a round-trip engineering between UML state machine and code, which means that modifications in code can be reflected back to model.}
	\end{cvitems}
}

\cventry
{Attendee at Summer School} % Role
{6th International Summer School on Domain Specific Modelling Theory and Practice (DSM-TP)} % Event
{Antwerp, Belgium} % Location
{Aug. 2015} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {Attended as a doctoral student. I learned different concepts and practices of MDE in this summer school such as model transformation, domain-specific modeling language design, mapping abstract and concrete syntax as well as the theory of temporal logic.}
	\end{cvitems}
}

\end{cventries}